---
title: "STAT 345 Final Project - Over and Over and Over and Over"
author: "STAT 345"
output: html_document
---

Expected Submission: You will generate a well-written R Markdown report that addresses the following prompts. This R Markdown report should source your analysis code and only display top-level, abstracted code _if/when appropriate_. Choices made during the analysis project should be described and justified in the report. 


Advice for getting started:

- Start a conversation chain with your group members. Email is a great place to start, but other options exist (texting, social media platforms, etc.). Set some reasonable expectations for how and when you plan to respond to conversations. It is likely going to be unacceptable to only respond once per week, for example, but also likely unacceptable to expect a response within the hour. Have an honest conversation with your group members about this issue.
- Start the project from a "top-down design" perspective. So, determine what the major steps of the process are, and determine what the inputs and outputs are for each of those steps (the output of step 1 will likely be the input for step 2, for example). This step is much like writing an outline for a paper before you start to write the paper itself, only much more valuable in a group setting. 
- Once you have a sense of the big picture (the outline), determine some "due dates" for each step of the process. Work backwards from the final submission date, giving yourselves time to work on each of the parts as needed. Given the top-down design, you should be able to "divide and conquer" -- working on parts of the project that depend on earlier steps.
- Decide how you plan to share code with each other. Using Git and GitHub is a really good choice here. If not, perhaps some form of shared directory online. In a worst-case scenario, email could also work. 
- Be prepared to give Dr. Baumann (at least) weekly updates on your progress. Some of this can be done via email, but discuss with your group about times you are each available to meet online as well (in an office-hour-like setting). Feel free to request meetings with Dr. Baumann to get help.

**General advice:** Get started early. If you wait to the last minute, it will not go well. For this project, you may find yourself spending a reasonable amount of time _searching_ for help.

1. Your first task is to create a list of top songs, dating back to 1958 (when Billboard introduced it's Hot 100 yearly chart). You may want to start with just the yearly top song, but your work should be general enough to account for multiple songs per year. You may narrow your search to a particular genre if you like. You may use any website that provides this information, though you may try to find one that makes part 2 as simple as possible.

2. For the top songs in part 1, gather some basic information: artist, title, year, genre (if appropriate), length, and other variables you think might be informative (sales figures, etc.).

3. Find a lyric hosting service (such as www.azlyrics.com or www.songlyrics.com, though these aren't the only options) that provides full lyrics to songs. Ideally, the URLs for these songs follow a reproducible pattern. Write a function that can automatically capture these song lyrics for your top songs from part 1, and then gather the lyrics. Do your best to keep this function general, but you may need to write code for specific instances.

4. Create two measures of song repetitiveness. Write a function (or two) to measure song repetitiveness, and apply it to each of the songs from part 1. Suggestions for "repetitiveness" include (but are definitely not limited to): "Do songs repeat the same phrase frequently?" and "Do songs repeat their song title frequently"

5. Have songs become more repetitive over time? Summarize and visualize your repetitive measures from part 4. 

6. (If possible) Extend your work to more songs! Consider more questions, like "Does genre matter?".

##Load Libraries

```{r}
library(tidyverse)
library(knitr)
library(rvest) # Web scraping tools.
```

##Collect Top Songs via Scraping

```{r}
##Scrape Wikipedia as it is easier? https://en.wikipedia.org/wiki/Billboard_Year-End_Hot_100_singles_of_2025

#Still have to add more songs not just the top song from each year


#Function to get the url for each year to get the top song from each year from Wiki. Input is year which is the year from the billboard hot 100 list. Output is tibble with title, artist, year, url from 1958 to 2025 of top 20 songs each year.
SongYear <- function(year) {

#Adjust the url to each year of top 100.
url <- paste0("https://en.wikipedia.org/wiki/Billboard_Year-End_Hot_100_singles_of_", year)

#Reads each website html content.
page <- read_html(url) 

# Used CSS selector to extract all tables on page.
# Uses first table as it is the top 100 list.
table <- page %>% 
  html_nodes("table.wikitable") %>% #Grabs all tables
  .[[1]] #Selects first table.

# Turns HTML table to data frame.
songs <- table %>%
    html_table() 

#Cleans and format data to get artist and title.
songs <- songs %>%
  select(2, 3) %>% #Keeps title and artist columns.
  rename(title = 1, artist = 2) %>% #Renames cols.
  slice(1:20) %>% #Grabs all 20 songs.
  mutate(year = year) %>% #Adds year of song as a col.
  mutate(title = str_replace_all(title, '"', "")) #Gets rid of quotation marks around the titles.

# Used CSS selector to find links to song titles which are in the second column and go to a hyper link.
# Used to extract song wiki page for more details, genre, lenght, etc.
links <- table %>% 
  html_nodes("td:nth-child(2) a") %>% #CSS selector for the title column link, a is used to get the clickable song link.
  html_attr("href") %>%  #Gets the hyperlink.
  url_absolute(url) # Update!!!

# Convert links into full urls by combining them with the song url pages.
#links[1:20] makes sure it grabs top 20 links.
songs$url <-links[1:20]

return(songs)
}

#Views results by calling the function.
songs <- map_dfr(1958:2025, SongYear)

songs
```


##Gather Data About the Top Songs (Artist, year, title, genre,...)

```{r}

#Function to scrape genre and song length from songs wiki url. Input is url which is the url of each songs wiki page. Output is a tibble that adds the genre and length to the other columns about each song.
song_info <- function(url) {
  
  #Reads each websites HTML content.
  page <- read_html(url)
  
  # Use CSS selector to find infobox on the songs that contain info on the genres and lenght, etc. TR grabs table row for the data.
  rows <- page %>%
    html_nodes("table.infobox tr")
  
  # Extract genre (find row containing "Genre")
  # keep() makes it so it only keeps the rows that contain word genre.
  # Converts each row into text to see if it contains Genre.
  # td makes it so we collect the data in the genre.
  genre <- rows %>%
    keep(~ str_detect(html_text(.x), regex("Genre", ignore_case = TRUE))) %>%
    html_node("td") %>% 
    html_text(trim = TRUE) %>%
    .[1] %>% #Makes it so it is a single first value
    str_replace_all("\n",", ") %>%
    str_squish() %>%
    str_replace_all("\\[\\d+\\]", "")
  
  # Extract song length similar to genre.
  song_length <- rows %>%
    keep(~ str_detect(html_text(.x), regex("Length", ignore_case = TRUE))) %>%
    html_node("td") %>%
    html_text(trim = TRUE) %>%
    .[1]
  
  # Makes it time format
  song_length <- str_extract(song_length, "\\d+:\\d+")
  
  #Returns results as a tibble(data frame)
  tibble(
    genre = ifelse(length(genre) == 0, NA, genre), #Deals with missing parts
    length = ifelse(length(song_length) == 0, NA, song_length))
}

#Apply functions to each song.
song_details <- map_dfr(songs$url, song_info)

#Combines original song data with new details.
songs <- bind_cols(songs, song_details)

songs
```


##Scrape lyrics from Song (Function that scrapes songs from Collect top songs)

```{r}

```


##Apply the lyrics Scrape function to top songs

```{r}

```


##Create Repetiveness Functions to Measure Repetiveness

```{r}
#Function 1: same phrase frequently
```

```{r}
#Function 2: repetition of song title:(May not do one of these)

#Function to measure how repetitive the songs are by seeing how often the title is said in the song. Input is lyrics and title which is the song lyrics and song title. Output is a repetition score which is from 0 to 1 with 1 being very repetitive.
title_repetitiveness <- function(lyrics, title) {
  
  # Convert all words to lowercase.
  lyrics <- tolower(lyrics)
  title <- tolower(title)
  
  # Remove punctuation from all lyrics.
  lyrics <- str_replace_all(lyrics, "[[:punct:]]", "")
  title <- str_replace_all(title, "[[:punct:]]", "")
  
  #Squish lyrics and title together to help avoid large spaces.
  lyrics <- str_squish(lyrics)
  title <- str_squish(title)
  
  # Regex pattern for multi word titles
  # \b is so there are boundaries and we match the phrase correctly.
  pattern <- paste0("\\b", str_replace_all(title, "\\s+", "\\\\s+"), "\\b")
  
  # Count total words
  total_words <- str_count(lyrics, "\\S+")
  
  # Count how many times title appears
  title_count <- str_count(lyrics, regex(pattern))
  
  # Normalize by length of song
  repetition_score <- title_count / total_words
  
  return(repetition_score)
}
```


##Apply Repetiveness Functions

```{r}

```


##Visualization using bar graph or another type to show repetition score

```{r}

```

##Interpretation of Graph(Summary):
- ...


##Make sure to adjust to make this work for more songs than just the top ones. Also question if genre matters.
